Sequential rank agreement methods for comparison of ranked lists

### 2015-04-21 latex/paper.Rnw
Fix for censoring

producelists <- function(x, y) {
    index <- seq(1, nrow(golub))
                                        # d <- data.frame(y, x)

@@

                                        # Elastic net
    X <- scale(t(x))
    enet <- glmnet(X, y, family="binomial", alpha=.8)
    nyres <- cv.glmnet(X, y, family="binomial", alpha=.8)
    coefficients <- coef(enet, s=nyres$lambda.1se)[-1]
    nonzeros <- sum(coefficients!=0)
    list3 <- order(abs(coefficients), decreasing=TRUE)

                                        # MIC
    MIC <- sapply(index, function(i) { mine(x[i,], y)$MIC})
    list4 <- order(MIC, decreasing=TRUE)

@@

res <- sqrt(sra(inputmatrix))

@@

\begin{figure}[tb]
\begin{center}
<<fig=TRUE,echo=FALSE>>=
ysize <- 1000
plot(res[1:ysize], lwd=3, col="red", type="l", ylim=c(0,1300), ylab="Sequential rank agreement", xlab="Depth")

## 
# col1 <- makeTransparent()
null <- sqrt(random_list_sra(inputmatrix, B=1, n=400))
## matlines(null[1:ysize,], col="gray", lty=1)

>>>>

producelists <- function(x, y) {
    nitems <- length(y)
    index <- seq(1, nrow(golub))
                                        # d <- data.frame(y, x)

@@

                                        # Elastic net
    X <- scale(t(x))
    enet <- glmnet(X, y, family="binomial", alpha=.8)
    nyres <- cv.glmnet(X, y, family="binomial", alpha=.8)
    coefficients <- coef(enet, s=nyres$lambda.1se)[-1]
    nonzeros <- sum(coefficients!=0)
    list3 <- order(abs(coefficients), decreasing=TRUE)
    if (nonzeros==0) {
        list3[(nonzeros+1):nitems] <- 0
    } 
                                        # MIC
    MIC <- sapply(index, function(i) { mine(x[i,], y)$MIC})
    list4 <- order(MIC, decreasing=TRUE)

@@

res <- sqrt(sra(inputmatrix, B=20))
inputmatrix2 <- inputmatrix
inputmatrix2[51:nrow(inputmatrix),] <- 0
res2 <- sqrt(sra(inputmatrix2, B=20))

@@

\begin{figure}[tb]
\begin{center}
<<fig=TRUE,echo=FALSE>>=
ysize <- 1000
plot(res[1:ysize], lwd=3, col="red", type="l", ylim=c(0,1300), ylab="Sequential rank agreement", xlab="Depth")
lines(res2[1:ysize], lwd=2, col="purple")
## 
# col1 <- makeTransparent()
null <- sqrt(random_list_sra(inputmatrix, B=1, n=400))
## matlines(null[1:ysize,], col="gray", lty=1)
